---
title: "Validation of Time-Frequency Analyses with Elastic Net feature selection and SVM classification"
output: html_notebook
---



```{r message=FALSE}

library(R.matlab)
library(sjmisc)
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(kernelboot)
library(pROC)
library(effsize)
library(e1071)
library(pracma)
library(verification)
library(progress)
library(caret)
library(LiblineaR)
library(groupdata2)
library(sparseSVM)
library(doParallel)
library(stringr)
library(glmnet)
library(glmnetUtils)
library(eNetXplorer)

```

## Participant numbers from experiment 2

```{r}

#Lists of participant numbers per groups, extracted from Excel file manually

CC_no_val = c('TVD_0001','TVD_0042','TVD_0277','TVD_0012','TVD_0016','TVD_0052','TVD_0070','TVD_0243','TVD_0229','TVD_0050','TVD_0256','TVD_0240','TVD_0145')

DC_no_val = c('TVD_0148','TVD_0144','TVD_0136','TVD_0127','TVD_0112','TVD_0104','TVD_0205','TVD_0010','TVD_0156','TVD_0059','TVD_0206','TVD_0620','TVD_0622','TVD_0624','TVD_0627')

Control_no_val = c('CO_0001_','CO_0004_','CO_0005_','CO_0006_','CO_0009_','CO_0010_','CO_0011_','CO_0012_','CO_0013_','CO_0014_','CO_0015_','CO_0016_','CO_0017_','CO_0018_','CO_0022_','CO_0023_','CO_0024_','CO_0025_','CO_0026_','CO_0029_','CO_0030_','CO_0031_','CO_0032_','CO_0033_','CO_0036_','CO_0037_','CO_0038_','CO_0039_')


```


## Loading data for all timepoints


```{r}


## Function to store all filenames of a directory with a certain pattern in a list

get_filelist <- function(wd, pattern) {
  setwd(wd)
  filelist = list()
  for (file in list.files(wd, pattern=pattern, all.files=FALSE, full.names=FALSE)){ #Extract all filenames from the given directory that match a given pattern
    filelist = append(filelist, file) #append each filename matching the pattern to the list
  }
  return(filelist)
}

# Function to transform the single matlab structure of each participant into one long dataframe with 15k cols and one row
transform_tf <- function(mat_structure, tf_df, scale){
  names = c()
  for (tp in seq_along(seq(39,dim(tf_df)[2],39))){ #iterate over timepoints; each 39th column is a new timepoint (39 freq values per timepoint)
    names = c(names, sapply(mat_structure[2][[1]], function(x) paste(tp, "ms", x, "hz", sep ="_"))) #Generate names based on timepoint and frequency
  }
  names(tf_df) <- names # Name Frequency*Timepoint columns of dataframe containing the ITPC and Power values (rows still exist as electrodes)
  tf_df$electrode <- sapply(mat_structure[3][[1]], unlist) # Name electrode column
  long <- tf_df %>% pivot_longer(!electrode, names_to = "frequency", values_to = "power") #Transform to long dataframe; the previously generate frequency*timepoint names are store in the "frequency" column
  names_full = paste(long$electrode, long$frequency, sep = "_") #generate names from columns for later use; Now the names are Electrode*Frequency*Timepoint
  if (scale) # Indicates whether data shall be scaled
    long <- scale(long[,3]) else #the third column contains the actual values, the other ones were just used to generate column names
    long <- long[,3]
  long[is.na(long)] <- 0 #NA values are assigned 0
  long <- data.frame(t(long)) #transpose and save as df
  names(long) <- names_full #assign previously generated names

  return(long)
}


# Function to assign Group Names based on participant number
get_group_val <- function(part_no){
  if (part_no %in% CC_no_val){ # Set group according to participant number
    group <- "CC"
  } else if (part_no %in% DC_no_val){
    group <- "DC"
  } else if (part_no %in% Control_no_val){
    group <- "Control"
  }
  group
}

## Function to write participant data from .mat files in an empty dataframe. The empty dataframe is filled participant by participant
write_files_to_list_val <- function(filelist, df_empty, scale = TRUE, rel = FALSE){


  for (no_file in seq_along(filelist)) { #iterate over position in filelist

    mat <- readMat(con = filelist[no_file]) # read .mat file from file position

    if (rel == TRUE){ # rel indicates whether RELative ower change shall be loaded, or ITPC
      mat_structure <- mat$totalpower.baselined.relchange # select relative power
      df_full <- data.frame(mat_structure[5]) # 5 is the position of powspctrm in matlab structure
    } else{
      mat_structure <- mat$totalpower.itpc.itlc # select itpc
      df_full <- data.frame(mat_structure[8]) # 8 is the position of itpc
      }

    part_no <- substr(filelist[no_file],28,35) #get participant number from filename
    group <- get_group_val(part_no) #get group from participant number
    long_df <- transform_tf(mat_structure,df_full, scale = scale)
    df_empty[no_file,] <- cbind(long_df, part_no, group) #assign each participant to one row
    names(df_empty) <- c(names(long_df), "part_no", "group")
    }

  output <- list("type" = ifelse(rel, "rel_power", "itpc"), "data" = df_empty)
  return(output)
}



```

# Reading and Transforming Dataframes: ITPC

Application of the previously defined functions to the files of cataracts / controls

```{r warning=FALSE}

# Instantiate empty dataframe of fitting size:
# 28 rows, one for each participant
# Number of columns: 32*39*71 +2
# 32 for 32 electrodes
# 39 for 1 Hz frequency bins from 2 to 40 Hz
# 71 for 20ms time bins from -700 to + 700 ms
# +2 for participant number and group

empty_cat <- data.frame(matrix(NA, nrow = 28, ncol = 32*39*71 +2))
empty_con <- empty_cat

scale = FALSE # Indicates whether the data should be scaled when loaded
rel = FALSE # Indicates whether relative power change shall be loaded, if not then ITPC is loaded

path <- paste("/home/bpn/Dokumente/Max/Data/Wavelet/wavelets_exp2/",
              ifelse(rel,"Rel_Power","ITPC"),
              sep = "")

#get filenames from cataract directory (indicated by "TVD")
filelist_cat_val <- get_filelist(path,"TVD")

#Write control dataframes to list of dataframes
cat_val <- write_files_to_list_val(filelist_cat_val, empty_cat, scale = scale, rel = rel)

#get filenames from cataract directory (indicated by "CO")
filelist_con_val <- get_filelist(path,"CO")

#Write control dataframes to list of dataframes
con_val <- write_files_to_list_val(filelist_con_val, empty_con, scale = scale, rel = rel)

```

# Reading and Transforming Dataframes: Relative Power Change

Application of the previously defined functions to the files of cataracts / controls

```{r warning=FALSE}

scale = FALSE # Indicates whether the data should be scaled when loaded
rel = TRUE # Indicates whether relative Data shall be loaded

path <- paste("/home/bpn/Dokumente/Max/Data/Wavelet/wavelets_exp2/",
              ifelse(rel,"Rel_Power","ITPC"),
              sep = "")

#get filenames from cataract directory
filelist_cat_val <- get_filelist(path,"TVD")

#Write control dataframes to list of dataframes
cat_rel_val <- write_files_to_list_val(filelist_cat_val,empty_cat, scale = scale, rel = rel)

#get filenames from cataract directory
filelist_con_val <- get_filelist(path,"CO")

#Write control dataframes to list of dataframes
con_rel_val <- write_files_to_list_val(filelist_con_val, empty_con, scale = scale, rel = rel)

```

# Combining cataracts and controls and combinign ITPC and Rel_Power into large DF

```{r}
nrows = 56 # 56 participants for experiment 2

# Explanation for number of columns: Same as when loading the data
total_pow_val <- data.frame(matrix(NA, nrow = nrows, ncol = 32*39*71+2))
total_itpc_val <- data.frame(matrix(NA, nrow = nrows, ncol = 32*39*71+2))

# The rows are filled first with cataract, and then with control individuals
total_itpc_val[1:(nrows/2),] <- cat_val$data
total_itpc_val[(nrows/2+1):nrows,] <- con_val$data
total_pow_val[1:(nrows/2),] <- cat_rel_val$data
total_pow_val[(nrows/2+1):nrows,] <- con_rel_val$data

names(total_pow_val) <- names(cat_rel_val$data)
names(total_itpc_val) <- names(cat_val$data)


# Select only posterior electrodes (by name)
post_pow_val <- total_pow_val
post_itpc_val <- total_itpc_val
post_pow_val <- post_pow_val[, grep(pattern="^TP9|CP5|CP1|CP2|CP6|TP10|P7|P3|Pz|P4|P8|O1|O2|part_no|group", colnames(post_pow_val))]
post_itpc_val <- post_itpc_val[, grep(pattern="^TP9|CP5|CP1|CP2|CP6|TP10|P7|P3|Pz|P4|P8|O1|O2|part_no|group", colnames(post_itpc_val))]


# Select only timepoints from -100 to 500 ms for analysis: -700ms = 1ms, 700 ms = 71ms, -100 = 31ms, 500 = 61ms
ms_string = sapply(c(31:61), function(x) paste(as.character(x),"_ms", sep =""))
analysis_pattern = paste(ms_string,collapse = "|")
analysis_pattern = paste(analysis_pattern, "part_no", "group", sep = "|")

analysis_pow_val <- post_pow_val[, grep(pattern=analysis_pattern, colnames(post_pow_val))]
analysis_itpc_val <- post_itpc_val[, grep(pattern=analysis_pattern, colnames(post_itpc_val))]


```

## Combining both ITPC and relative power data into one dataframe for combined domain analyses

```{r}

# Preprocess ITPC and Power
itpc_comb_val <- analysis_itpc_val[,-c((ncol(analysis_itpc_val)-1) : ncol(analysis_itpc_val))] # Drop last two columns
pow_comb_val <- analysis_pow_val[,-c((ncol(analysis_pow_val)-1) : ncol(analysis_pow_val))]  # Drop last two columns
col_names_val <- names(itpc_comb_val) # Extract names

# Normalize over all participants; needed as data is on different scales
norm_image <- function(x) (x - mean(as.matrix(x))) / sd(as.matrix(x))
itpc_comb_val <- norm_image(itpc_comb_val)
pow_comb_val <- norm_image(pow_comb_val)

# Combining both dataframes, and add the two columns participant number and group
itpc_power_val <- cbind(itpc_comb_val, pow_comb_val, analysis_itpc_val[,c((ncol(analysis_itpc_val)-1) : ncol(analysis_itpc_val))])
names(itpc_power_val) <- c(paste("itpc", names(itpc_comb_val), sep = "_"), paste("pow", names(pow_comb_val), sep = "_"),"part_no","group")

# Sanity check: Mean and SD of combined dataframe, should be 0 and 1 or very close
mean(as.matrix(itpc_power_val[,-c((ncol(itpc_power_val)-1) : ncol(itpc_power_val))]))
sd(as.matrix(itpc_power_val[,-c((ncol(itpc_power_val)-1) : ncol(itpc_power_val))]))



```

# Functions for Validation

```{r}


### Transform each dataframe according to needs
transform_df <- function(data, control = TRUE) {

  data <- data %>% mutate(isCC = factor(group != 'CC', labels = c("yes","no"))) # Build new column that indicates whether a participant is CC or not
  data$group <- factor(data$group, levels = c("CC", "DC", "Control"))

  if (control == FALSE) {

    data <- data[data$group %in% c('DC','CC'),] #subset only CC and DC individuals f control == F

  } else {

    data <- data

  }

  data <- data %>% dplyr::select(-c(part_no, group))

  return(data)

}

## Cross-Validation of e1071 SVM with selected features
load_model <- function(itpc_ = itpc, control_ = control, combined_ = combined){

  # Assign name to domain to load correct data based on input
  if(combined_)
    domain = "combined_" else
      domain = ifelse(itpc_, "itpc_", "pow_")

  group <- ifelse(control_, "control","dc")

  # Load weights
  results_final <- readRDS(paste("Final_RDS_files/weights_",
                                 domain,
                                 group,
                                 ".RDS", sep = ""))

  # Load features selected in feature selection procedure
  coefs <- readRDS(paste("Final_RDS_files/final_features_",
                         domain,
                         group,
                         ".RDS", sep = ""))$coefs

  selected_features = coefs@Dimnames[[1]][which(coefs != 0)]
  selected_features = c(selected_features[2:length(selected_features)],"isCC")

  output <- list("weights" = results_final$weights, "selected_features" = selected_features, "threshold" = results_final$threshold)
}


# Function to determine significance of AUC with Mann-Whitney-U-Test
auc_wmw <- function(response, scores){

  labels <- as.logical(response)
  pos <- scores[labels]
  neg <- scores[!labels]
  wilcox.test(pos, neg)$p.value

}


# Function to load data, derive a classifier from loaded weights and obtain an ROC curve with p-value for AUC
validation <- function(itpc_ = itpc, control_ = control, combined_ = combined, only_new = F){

  # Load model according to input
  exp1 <- load_model(itpc_,control_,combined_)

  #Choose dataframe according to input
  if (itpc_)
    df <- transform_df(analysis_itpc_val, control = control_) else
      df <- transform_df(analysis_pow_val, control = control_)

  if (combined_)
    df <- transform_df(itpc_power_val, control = control_)

  # Check if only paticipants shall be included that are unique to experiment 2
  if(only_new) {
    new_indices <- analysis_itpc_val$part_no %in% all_new #all_new is a list defined when needed; only_new = T would thus throw an error if called too early
    df <- df[new_indices,]
  }

  # Subset selected features
  df = df[exp1$selected_features]

  # Derive classifier and build ROC analysis
  weights <- as.vector(exp1$weights)
  weights_as_rows <- do.call(rbind,
                             replicate(dim(df)[1],
                                       weights,
                                       simplify=FALSE))
  clf_val <- rowSums(df[,-ncol(df)]*weights_as_rows)
  response_val <- ifelse(df$isCC == "yes",1,0)
  rocObject <- roc(response_val,
                   clf_val,
                   print_auc = TRUE,
                   quiet = TRUE,
                   ci = TRUE)

  p <- auc_wmw(response_val,clf_val) # p-value from WMW Test
  sens_spec = coords(rocObject, exp1$threshold, input = "threshold", transpose = TRUE) #Get sensitivity and specificity at best threshold from exp 1

  return(list("roc" = rocObject, "p_val" = p, "sens_spec" = sens_spec, "thresh" = exp1$threshold))

}


# Function to plot ROC curve
plot_curve <- function(validation, control){

  # Set options: Square plot and do not show progress bar during bootstrapping
  par(pty = "s")
  options(pROCProgress = list(name = "none"))

  # Plot ROC curve from ROC object with custom text that shows the AUC, the p-value and the CIs
  plot_roc_val <- plot.roc(validation$roc,
                           percent=TRUE,
                           print.auc = TRUE,
                           print.auc.pattern = paste("  AUC = %.3f\n [%.3f - %.3f]","\n     p",
                                                     ifelse(validation$p_val<0.001," < 0.001",paste("=",round(validation$p_val,3)))),
                           print.thres = validation$thresh,
                           print.thres.pattern = "",
                           smooth=FALSE,
                           col=ifelse(control, "#009e73", "#8da0cb"))
  plot(ci.se(plot_roc_val, specificities=seq(0, 1, 0.01)), type="shape", no.roc = TRUE, col=ifelse(control, "#009e7322", "#8da0cb22"), border = 0, quiet = T)

}






```


## Validation - Experiment 2


```{r warning=FALSE}

## Single Domains ##
control = TRUE

# ITPC CC vs. Non-CC
val_itpc_all <- validation(T,control,F)
plot_curve(val_itpc_all,control)

# Power CC vs. Non-CC
val_pow_all <- validation(F,control,F)
plot_curve(val_pow_all,control)

control = FALSE

# ITPC CC vs. DC
val_itpc_dc <- validation(T,control,F)
plot_curve(val_itpc_dc,control)

# Power CC vs. DC
val_pow_dc <- validation(F,control,F)
plot_curve(val_pow_dc,control)

## Combined ##
control = TRUE

# Combined CC vs. Non-CC
val_combined_all <- validation(T,T,T)
plot_curve(val_combined_all,control)

control = FALSE

# Combined CC vs. DC
val_combined_dc <- validation(T,F,T)
plot_curve(val_combined_dc,control)

```


## Validation - only participants unique to experiment 2



```{r}

# Participant IDs per experiment

## Experiment 1
CC_1 = c("TVD_0001", "TVD_0012", "TVD_0015", "TVD_0016", "TVD_0042", "TVD_0052", "TVD_0070", "TVD_0243", "TVD_0274", "TVD_0240", "TVD_0256", "TVD_0050")

DC_1 = c("TVD_0200", "TVD_0206", "TVD_0144", "TVD_0177", "TVD_0136", "TVD_0181", "TVD_0127", "TVD_0156", "TVD_0205", "TVD_0010", "TVD_0148", "TVD_0135", "TVD_0606")

## Experiment 2
CC_2 = c('TVD_0001','TVD_0042','TVD_0277','TVD_0012','TVD_0016','TVD_0052','TVD_0070','TVD_0243','TVD_0229','TVD_0050','TVD_0256','TVD_0240','TVD_0145')

DC_2 = c('TVD_0148','TVD_0144','TVD_0136','TVD_0127','TVD_0112','TVD_0104','TVD_0205','TVD_0010','TVD_0156','TVD_0059','TVD_0620','TVD_0622','TVD_0624','TVD_0627','TVD_0206')

# Build function to subset IDs
`%notin%` <- Negate(`%in%`)

# Select participants that are not included in experiment 1
CC_new = c()
for (i in CC_2) if (i %notin% CC_1) CC_new = append(CC_new, i)

DC_new = c()
for (i in DC_2) if (i %notin% DC_1) DC_new = append(DC_new, i)

# Select all Controls for comparability to Suddha's study
for (i in Control_no_val) Control_new = append(Control_new, i)

# Combine IDs of all participants new to experiment 2
all_new = c(CC_new, DC_new, Control_new)


## Single Domains ##

control = TRUE

#ITPC CC vs. Non-CC
val_itpc_all_new <- validation(T,T,F,only_new = T)
plot_curve(val_itpc_all_new, control)

#Power CC vs. Non-CC
val_pow_all_new <- validation(F,T,F,only_new = T)
plot_curve(val_pow_all_new, control)

control = FALSE

#ITPC CC vs. DC
val_itpc_dc_new <- validation(T,F,F,only_new = T)
plot_curve(val_itpc_dc_new, control)

#Power CC vs. DC
val_pow_dc_new <- validation(F,F,F,only_new = T)
plot_curve(val_pow_dc_new, control)


## Combined Domains ##

#Combined CC vs. Non-CC
val_combined_all_new <- validation(T,T,T,only_new = T)
plot_curve(val_combined_all_new, T)

#Combined CC vs. DC
val_combined_dc_new <- validation(T,F,T,only_new = T)
plot_curve(val_combined_dc_new, F)


```

# Exploratory Analysis:

Validating CC vs. Non-CC classification with Power features selected for CC vs. DC classification, to check whether low AUC value in CC vs. Non-CC results from the low number of selected features

```{r}

validation_exploratory <- function(itpc_ = itpc, control_ = control, combined_ = combined, only_new = F){

  # Load model trained for CC vs. DC classification, regardless of "control_" input;
  # the rest of the function is similar to the validation function defined above
  exp1 <- load_model(itpc_,control = F,combined_)

  #Choose dataframe
  if (itpc_)
    df <- transform_df(analysis_itpc_val, control = control_) else
      df <- transform_df(analysis_pow_val, control = control_)

  if (combined_)
    df <- transform_df(itpc_power_val, control = control_)

  if(only_new) {
    new_indices <- analysis_itpc_val$part_no %in% all_new
    df <- df[new_indices,]
  }

  df = df[exp1$selected_features]

  weights <- as.vector(exp1$weights)
  weights_as_rows <- do.call(rbind,
                             replicate(dim(df)[1],
                                       weights,
                                       simplify=FALSE))
  clf_val <- rowSums(df[,-ncol(df)]*weights_as_rows)
  response_val <- ifelse(df$isCC == "yes",1,0)
  rocObject <- roc(response_val,
                   clf_val,
                   print_auc = TRUE,
                   quiet = TRUE,
                   ci = TRUE)

  p <- auc_wmw(response_val,clf_val) # p-value from WMW Test
  sens_spec = coords(rocObject, exp1$threshold, input = "threshold", transpose = TRUE)

  return(list("roc" = rocObject, "p_val" = p, "sens_spec" = sens_spec, "thresh" = exp1$threshold))

}

val_pow_all <- validation_exploratory(F,T,F)
plot_curve(val_pow_all,T)
```

